\section{jstat命令}
\label{chap:tools_jstat}

监控JVM统计数据。


\begin{lstlisting}[language=cshell]

jstat [ generalOption | outputOptions vmid [ interval[s|ms] [ count ] ]

\end{lstlisting}


-generalOption

单个通用命令行选项；可选参数为 -help 和 -options


outputOptions

输出选项，可以配置-t, -h, and -J 选项使用



-statOption

可以使用-options选项输出支持的统计选项


\begin{itemize}

    \item class: Displays statistics about the behavior of the class loader.

    \item compiler: Displays statistics about the behavior of the Java HotSpot VM Just-in-Time compiler.

    \item gc: Displays statistics about the behavior of the garbage collected heap.

    \item gccapacity: Displays statistics about the capacities of the generations and their corresponding spaces.

    \item gccause: Displays a summary about garbage collection statistics (same as -gcutil), with the cause of the last and current (when applicable) garbage collection events.

    \item gcnew: Displays statistics of the behavior of the new generation.

    \item gcnewcapacity: Displays statistics about the sizes of the new generations and its corresponding spaces.

    \item gcold: Displays statistics about the behavior of the old generation and metaspace statistics.

    \item gcoldcapacity: Displays statistics about the sizes of the old generation.

    \item gcmetacapacity: Displays statistics about the sizes of the metaspace.

    \item gcutil: Displays a summary about garbage collection statistics.

    \item printcompilation: Displays Java HotSpot VM compilation method statistics.
    
\end{itemize}


-gc option

\begin{itemize}
    \item S0C: Current survivor space 0 capacity (kB).

    \item S1C: Current survivor space 1 capacity (kB).
    
    \item S0U: Survivor space 0 utilization (kB).
    
    \item S1U: Survivor space 1 utilization (kB).
    
    \item EC: Current eden space capacity (kB).
    
    \item EU: Eden space utilization (kB).
    
    \item OC: Current old space capacity (kB).
    
    \item OU: Old space utilization (kB).
    
    \item MC: Metaspace capacity (kB).
    
    \item MU: Metacspace utilization (kB).
    
    \item CCSC: Compressed class space capacity (kB).
    
    \item CCSU: Compressed class space used (kB).
    
    \item YGC: Number of young generation garbage collection events.
    
    \item YGCT: Young generation garbage collection time.
    
    \item FGC: Number of full GC events.
    
    \item FGCT: Full garbage collection time.
    
    \item GCT: Total garbage collection time.
\end{itemize}